Evaluation of the repository

### 2024-12-03 pages/paper_evaluation.qmd
feat(table): generate table of applicable criteria for stars/reporting

```{python}
# Imports and functions
import pandas as pd
import plotly.express as px
import plotly.express as px
import plotly.io as pio
from functions import eval_chart, plot_scatter, calculate_scores
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 5, 4, 1],
  'Lim et al. 2020': [15, 3, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [16, 1, 2, 5],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021': [11, 2, 2, 3],
  'Huang et al. 2019': [7, 2, 7, 2],
  'Lim et al. 2020': [12, 0, 4, 2],
  'Kim et al. 2021': [12, 0, 5, 1],
  'Anagnostou et al. 2022': [8, 3, 4, 3],
  'Johnson et al. 2021': [15, 0, 2, 1],
  'Hernandez et al. 2015': [10, 0, 7, 1],
  'Wood et al. 2021': [13, 0, 4, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

>>>>

```{python}
# Imports and functions
import pandas as pd
import plotly.express as px
import plotly.express as px
import plotly.io as pio
from functions import (eval_chart, plot_scatter, calculate_scores,
                       calculate_percentage, extract_reproduced)
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021 (16/17)': [17, 6, 1, 0],
  'Huang et al. 2019 (3/8)': [14, 5, 4, 1],
  'Lim et al. 2020 (9/9)': [15, 3, 3, 3],
  'Kim et al. 2021 (10/10)': [15, 5, 2, 2],
  'Anagnostou et al. 2022 (1/1)': [14, 2, 5, 3],
  'Johnson et al. 2021 (4/5)': [16, 1, 2, 5],
  'Hernandez et al. 2015 (1/8)': [18, 2, 3, 1],
  'Wood et al. 2021 (5/5)': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
ispor_dict = {
  'Shoaib and<br>Ramamohan 2021 (16/17)': [11, 2, 2, 3],
  'Huang et al. 2019 (3/8)': [7, 2, 7, 2],
  'Lim et al. 2020 (9/9)': [12, 0, 4, 2],
  'Kim et al. 2021 (10/10)': [12, 0, 5, 1],
  'Anagnostou et al. 2022 (1/1)': [8, 3, 4, 3],
  'Johnson et al. 2021 (4/5)': [15, 0, 2, 1],
  'Hernandez et al. 2015 (1/8)': [10, 0, 7, 1],
  'Wood et al. 2021 (5/5)': [13, 0, 4, 1]
}
ispor_wide = pd.DataFrame(ispor_dict, index=col).T

@@

## Table with proportion of applicable reporting criteria that were fully met

This is part of a table used in the journal article:

```{python}
# Calculate essential and optional percentages
report_df = pd.DataFrame({
    'stress': calculate_percentage(stress_wide),
    'generic': calculate_percentage(ispor_wide)
})

# Calculate percentage and items in scope
report_df['percentage'], report_df['num'], report_df['denom'] = zip(
  *report_df.index.to_series().apply(extract_reproduced))

# Sort by percentage and then by number of items in scope
report_df = report_df.sort_values(by=['percentage', 'denom'],
                                  ascending=[False, False])

# Create formatted column with % and n/n reproduced
report_df['reproduction'] = report_df.apply(
    lambda row: f"{row['percentage']}% ({row['num']}/{row['denom']})", axis=1
)

# Filter to relevant columns, save and display
report_applicable = report_df[['reproduction', 'stress', 'generic']]
report_applicable.to_csv('../data/applicable_report.csv')
report_applicable
```

### 2024-12-03 pages/repo_evaluation.qmd
docs(various): tweaks to images (white space, labels), protocol (organisation) and references.bib
feat(table): generate table of applicable criteria for stars/reporting

```{python}
# Imports and function
import plotly.express as px
import plotly.io as pio
import pandas as pd
from functions import eval_chart, plot_scatter
```

@@

@@

>>>>

```{python}
# Imports and function
import plotly.express as px
import plotly.io as pio
import pandas as pd
from functions import (eval_chart, plot_scatter,
                       calculate_percentage, extract_reproduced)
```

@@

## Table with proportion of applicable STARS criteria that were fully met

This is part of a table used in the journal article:

```{python}
# Calculate essential and optional percentages
stars_df = pd.DataFrame({
    'stars_essential': calculate_percentage(essential_wide),
    'stars_optional': calculate_percentage(optional_wide)
})

# Calculate percentage and items in scope
stars_df['percentage'], stars_df['num'], stars_df['denom'] = zip(
  *stars_df.index.to_series().apply(extract_reproduced))

# Sort by percentage and then by number of items in scope
stars_df = stars_df.sort_values(by=['percentage', 'denom'],
                                ascending=[False, False])

# Create formatted column with % and n/n reproduced
stars_df['reproduction'] = stars_df.apply(
    lambda row: f"{row['percentage']}% ({row['num']}/{row['denom']})", axis=1
)

# Filter to relevant columns, save and display
stars_applicable = stars_df[['reproduction', 'stars_essential', 'stars_optional']]
stars_applicable.to_csv('../data/applicable_stars.csv')
stars_applicable
```

@@

# Reduce white space
stars_chart.update_layout(
    margin=dict(l=0, r=0, t=10, b=0)
)
